\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}%Encoding
\usepackage{graphicx}% Incluye archivos de imagenes
\usepackage{dcolumn}% Alinea tablas al punto decimal
\usepackage{bm}% Bold math
\usepackage[english]{babel}%Definición de idioma
%\usepackage{gensymb} %Generador de símbolos
\usepackage{float} %Ajustar floats
\usepackage{hhline}
%\usepackage{bbding}
%\newdate{date}{10}{05}{2013}
%\date{\displaydate{date}}

\begin{document}

\begin{center}
\Huge
Phenomenological Study of Heavy Neutrinos at the LHC, through High-mass Resonance, using the Vector Boson Fusion Technique

\vspace{3mm}
\Large Carlos Miguel Patiño Paz

\large
201224993


\vspace{2mm}
\Large
Director: Andrés Flórez

\normalsize
\vspace{2mm}

\today
\end{center}


\normalsize
\include{Introduction/introduction}
\include{Objectives/objectives}
\include{ComputationalResources/computationalResources}
\include{MadGraph/madgraph}
\include{Definitions/definitions}
\include{Results/results}




\begin{thebibliography}{10}

\bibitem {Detectores}Particle Data Group, Olive, K. A. et al. , Chin.Phys. C38, 090001 (2014)


\bibitem{Super-Kamiokande} Fukuda, S. et al. (2003) Nuclear Instruments and Methods in Physics Research A 501 (2003) 418–462

\bibitem{KamLAND} Decowski, M. (2016). KamLAND's precision neutrino oscillation measurements. Nuclear Physics B, 908, pp.52-61.

\bibitem{K2K} K2K Collaboration: Aliu, E. et al (2005). Evidence for Muon Neutrino Oscillation in an Accelerator-Based Experiment. Physical Review Letters, 94(8).

\bibitem {Experimentos}Nakamura, K. et al. (2010) (Particle Data Group), J. Phys. G 37, 075021 (2010) 

\bibitem {See-saw} Deppisch, F., Bhupal Dev, P., \& Pilaftsis, A. (2015). Neutrinos and collider physics. New Journal Of Physics, 17(7), 075019. http://dx.doi.org/10.1088/1367-2630/17/7/075019

\bibitem {LEP} Abdesslam, A. et al. (2014) Type II Seesaw Higgsology and LEP/LHC constraints. arXiv:1411.5645 [hep-ph]

\bibitem {CMS ATLAS} Khachatryan, V., Sirunyan, A., Tumasyan, A., Adam, W., Asilar, E., \& Bergauer, T. et al. (2016). Search for heavy Majorana neutrinos in $e\pm e\pm +$ jets and $e\pm$ $\mu \pm +$ jets events in proton-proton collisions at s = 8 $\sqrt{s}=8$ TeV. Journal Of High Energy Physics, 2016(4).

\bibitem {VBF Search} Brooke, J., Buckley, M., Dunne, P., Penning, B., Tamanas, J., \& Zgubič, M. (2016). Vector boson fusion searches for dark matter at the LHC. Physical Review D, 93(11). http://dx.doi.org/10.1103/physrevd.93.113013

\bibitem{MadGraph} Alwall, J., Herquet, M., Maltoni, F., Mattelaer, O., \& Stelzer, T. (2011). MadGraph 5: going beyond. Journal Of High Energy Physics, 2011(6). http://dx.doi.org/10.1007/jhep06(2011)128

\bibitem{Pythia}Sjöstrand, T., Ask, S., Christiansen, J., Corke, R., Desai, N., \& Ilten, P. et al. (2015). An introduction to PYTHIA 8.2. Computer Physics Communications, 191, 159-177. http://dx.doi.org/10.1016/j.cpc.2015.01.024

\bibitem{Delphes} de Favereau, J., Delaere, C., Demin, P., Giammanco, A., Lemaître, V., Mertens, A., \& Selvaggi, M. (2014). DELPHES 3: a modular framework for fast simulation of a generic collider experiment. Journal Of High Energy Physics, 2014(2). http://dx.doi.org/10.1007/jhep02(2014)057

\bibitem{ROOT} Antcheva, I., Ballintijn, M., Bellenot, B., Biskup, M., Brun, R., \& Buncic, N. et al. (2009). ROOT — A C++ framework for petabyte data storage, statistical analysis and visualization.

\end{thebibliography}

\vspace{1.5cm}

\section*{Firma del Director}
\vspace{1.5cm}

\section*{Firma del Estudiante	}



\end{document} 
